### 2024-06-13 README.Rmd
Update README

> Czapanskiy MF, Santora JA, Dietrich KS, Cimino MA, Hazen EL, Reiss CS, Veit RR (2024). _`r Title`_. Marine Ecology Progress Series <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console

>>>>

> Czapanskiy MF, Santora JA, Dietrich KS, Cimino MA, Hazen EL, Reiss CS, Veit RR (2024). _`r Title`_. Marine Ecology Progress Series <https://doi.org/10.3354/meps14609>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder: scripts](/analysis/scripts): R scripts for processing data and performing the analysis
  - [:file\_folder: data](/analysis/data): Raw and derived data

@@

You can download the compendium as a zip from from this URL:
[main.zip](/archive/main.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- download the raw data (see [/analysis/data/raw_data/README.md](/analysis/data/raw_data/README.md))
- run all the data processing and analysis scripts (run [/analysis/scripts/_make_all.R](/analysis/scripts/_make_all.R))
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`
